Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data

### 2021-08-10 paper.Rmd
Tons of stuff

# setwd(dir.script)
source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
# source("fdaDelta.R")
```

@@

One possibility to address te problem of a pointwise analysis is to treat curves as single objects rather than as a series of unconnected points [Ramsay & Silverman, 2005]. Røislien et al. [2012] presented a method that extends the Limits of Agreement (LoA) concept [11] to functional data. This is achieved by approximating curves using Fourier series and resampling the thus obtained functions. The approach accounts for the autocorrelation characteristic in the signal and at the same time allows for an intuitive description of the systematic and random error terms in the original sampling space (e.g. actual degrees). Røislien et al. [10], however, make a number of strong assumptions, which are often not or only partially fulfilled in empirical data sets:

@@

* v1.1 : Functional data version of v1

@@

@@

#### v1 (n = length(subjects) random strides from all strides)

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v1")
floa.point <- floa_point(data)

cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all")

plot_cov_ver(cover.cross.v1)
```

#### V2 (One random stride per subject)

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v2")
floa.point <- floa_point(data)

cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all")

plot_cov_ver(cover.cross.v2)
```

#### v3 (Fetch a SINGLE random stride from all strides)

```{r echo = FALSE, warning = FALSE, message = FALSE}
floa <- floa_rcb(data, n.boot, ver = "v3")
floa.point <- floa_point(data)

cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all")

plot_cov_ver(cover.cross.v3)
```

@@

>>>>

# setwd(dir.script)
source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/pick_subwise_curves.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/floa_roislien.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
```

@@

One possibility to address te problem of a pointwise analysis is to treat curves as single objects rather than as a series of unconnected points [Ramsay & Silverman, 2005]. Røislien et al. [2012] presented a method that extends the Limits of Agreement (LoA) concept [11] to functional data. This is achieved by approximating curves using Fourier series and resampling the thus obtained functions.

<!-- Anwendung der Argumentation der Reviewer* auf die "Roislien_FLoA": In Roislien et al. werden 95% Konfidenzintervalle gebootstrapped. The authors are producing the arithmetic mean curves, the variability of which will reflect variation between means. It is the variability of individual values that is relevant, and the limits will be too narrow by a factor of approximately the square root of n.subj. -->

The approach accounts for the autocorrelation characteristic in the signal and at the same time allows for an intuitive description of the systematic and random error terms in the original sampling space (e.g. actual degrees). Røislien et al. [10], however, make a number of strong assumptions, which are often not or only partially fulfilled in empirical data sets:

@@

@@

* v4 : Roislien approach (Get one random stride from each subject ONCE and boot-
       strap the resulting sample (of length (n=length(subjects))

@@

### Leave-one-out cross validation

n.boot <- 100
cover.cross <- crossval_coverage(data, n.boot)

plot_cov_ver(cover.cross)
```

<!-- #### v1 (n = length(subjects) random strides from all strides) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- data <- example_data(dat = "smooth", dir.data) -->
<!-- ``` -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v1") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v1) -->
<!-- ``` -->

<!-- #### V2 (One random stride per subject) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v2") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v2) -->
<!-- ``` -->

<!-- #### v3 (Fetch a SINGLE random stride from all strides) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v3") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v3) -->
<!-- ``` -->

@@

Anwendung der Argumentation der Reviewer* auf die "Roislien_FLoA": In Roislien et al. werden 95% Konfidenzintervalle gebootstrapped. The authors are producing the arithmetic mean curves, the variability of which will reflect variation between means. It is the variability of individual values that is relevant, and the limits will be too narrow by a factor of approximately the square root of n.subj.
